The Journey from Wild to Textbook Data: A Case Study from the National Longitudinal Survey of Youth

### 2021-09-25 paper/paper-jsdse/paper-jsdse.tex
racism not race

Singer and Willett (2003) used the wages and other variables of high school dropouts from the NLSY79 data as an example data set to illustrate longitudinal data modeling of wages on workforce experience, with covariates education and race. Our aim is to refresh this textbook data with data from 1994 through to the latest data reported in 2018. Here, we investigate the process of getting from the raw NLSY79 data to a textbook data set as similar as possible to that provided by Singer and Willett (2003). We should also note that race is a variable in the original data set, and for the purposes of studying racism, not race(T. 1998), it also provided with the refreshed data.

@@

@@

\leavevmode\hypertarget{ref-racismnotrace}{}%
T., Fullilove M. 1998. {``Comment: Abandoning "Race" as a Variable in Public Health Research--an Idea Whose Time Has Come.''} \emph{American Journal of Public Health} 88 (9): 1297--98.

>>>>

Singer and Willett (2003) used the wages and other variables of high school dropouts from the NLSY79 data as an example data set to illustrate longitudinal data modeling of wages on workforce experience, with covariates education and race. Our aim is to refresh this textbook data with data from 1994 through to the latest data reported in 2018. Here, we investigate the process of getting from the raw NLSY79 data to a textbook data set as similar as possible to that provided by Singer and Willett (2003). We should also note that race is a variable in the original data set, and for compatibility it is also provided with the refreshed data, for the purposes of studying racism, not race (Fullilove 1998),

@@

\leavevmode\hypertarget{ref-racismnotrace}{}%
Fullilove, M. T. 1998. {``Comment: Abandoning "Race" as a Variable in Public Health Research--an Idea Whose Time Has Come.''} \emph{American Journal of Public Health} 88 (9): 1297--98.

@@

### 2021-09-25 paper/paper.Rmd
racism not race

@SingerJudithD2003Alda used the wages and other variables of high school dropouts from the NLSY79 data as an example data set to illustrate longitudinal data modeling of wages on workforce experience, with covariates education and race. Our aim is to refresh this textbook data with data from 1994 through to the latest data reported in 2018. Here, we investigate the process of getting from the raw NLSY79 data to a textbook data set as similar as possible to that provided by @SingerJudithD2003Alda. We should also note that race is a variable in the original data set, and for the purposes of studying racism, not race[@racismnotrace], it also provided with the refreshed data. <!--However, we cannot create the exact same data set as published in their book since we do not have the information of what age threshold they used to determine the high school dropouts.-->

>>>>

@SingerJudithD2003Alda used the wages and other variables of high school dropouts from the NLSY79 data as an example data set to illustrate longitudinal data modeling of wages on workforce experience, with covariates education and race. Our aim is to refresh this textbook data with data from 1994 through to the latest data reported in 2018. Here, we investigate the process of getting from the raw NLSY79 data to a textbook data set as similar as possible to that provided by @SingerJudithD2003Alda. We should also note that race is a variable in the original data set, and for compatibility it is also provided with the refreshed data, for the purposes of studying racism, not race [@racismnotrace],  <!--However, we cannot create the exact same data set as published in their book since we do not have the information of what age threshold they used to determine the high school dropouts.-->
